### 2016-05-19 paper.tex
Update on Overleaf.

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

%\aclfinalcopy % Uncomment this line for the final submission
\input{bit-aclfinalcopy}
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.
\usepackage[noinline,nomargin,noindex,draft]{fixme}
\fxsetup{theme=color,mode=multiuser}
\FXRegisterAuthor{n}{note}{NOTE} 
%\nnote[inline]{this is how to make regular notes...}
%\nerror[margin]{} or \fxerror[inline]{reserved for final paper}

\newcommand\BibTeX{B{\sc ib}\TeX}

\title{Instructions for ACL-2016 Proceedings}

\author{Egon W.~Stemle \\
  EURAC \\
  Bozen-Bolzano, Italy \\
  {\tt egon.stemle@eurac.edu}} % \\\And
  %Jennifer-Carmen Frey \\
  %EURAC \\
  %Bozen-Bolzano, Italy \\
  %{\tt jennifercarmen.frey@eurac.edu} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
    This article describes the system that participated in the Part-of-speech
    tagging subtask of the \emph{EmpiriST 2015 shared task on automatic
    linguistic annotation of computer-mediated communication / social
    media}.

    The system combines a small assertion of trending techniques -- that
    implement matured methods -- from natural language processing to achieve
    competitive results on POS tagging of German CMC and web corpus data; 
    in particular, the system uses word embeddings and character-level representations of word beginnings and endings in a LSTM recurrent neural
    network architecture.

    %fixme: \fxerror[inline]{}write something about the results.

\end{abstract}

\section{Introduction}
\label{sec:intro}

Part-of-speech tagging (and tokenization) is an essential processing stage for virtually all NLP applications. However, for German there has been relatively little work in this area so far. To this end, the EmpiriST shared task (ST) focuses on tokenization and part-of-speech tagging~\cite{empirist2016}.

% Is POS tagging a solved task\cite{Giesbrecht2009}.
Recently, State-of-the-art results on various linguistic tasks were accomplished by architectures using neural-network based word embeddings; Baroni~\shortcite{baroni-dinu-kruszewski:2014:P14-1} conducted a set of experiments comparing the popular \texttt{word2vec}~\cite{DBLP:journals/corr/abs-1301-3781,arXiv:1310.4546} implementation for creating word embeddings to other recent distributional methods with state-of-the-art results across various (semantic) tasks.
Even though these results suggest that the word embeddings substantially outperform the recent architectures on semantic similarity and analogy detection tasks Levy~\shortcite{TACL570} conducted a comprehensive set of experiments and comparisons that suggest that much of the improved results are due to the system design and parameter optimizations, rather than the selected method;
they conclude that "there does not seem to be a consistent significant advantage to one approach over the other".

We take these results to use \texttt{word2vec} word embeddings in our architecture because they are (1) often faster to learn, and (2) for educational purposes, i.e.~we wanted to get some experience in using them.

\section{Design}
\label{sec:design}
Our overall design takes inspiration from as far back as Benello~\shortcite{Benello1989} who used a few preceding and one following word in a feed-forward network with back-propagation for PoS tagging; they achieved an accuracy of $0.95$ on the Brown Corpus.

Further inspiration comes from dos Santos~\shortcite{santos2014learning} who used a deep neural network trained with character-level joint with word embedding representation of words for PoS tagging. On the Wall Street Journal (WSJ) portion of the Penn Treebank they achieve accuracy scores of $0.9732$.

Our design comprises character-level 3-grams of word beginnings and ends joint with word embedding representation of words in a long short-term memory (LSTM) recurrent neural network (RNN) architecture~\cite{Hochreiter:1997:LSM:1246443.1246450} for learning a mapping of sequences of these representations to PoS tags.

\section{Implementation}
\label{sec:implementation}

We maintain the implementation in a source code repository at \url{https://github.com/iiegn/bot_zen}. 
The version tagged as {\tt 0.9} comprises the version that was used to generate the results submitted to the ST; 
the version tagged as {\tt 1.0} is identical at its core but comes with explicit documentation on how to download and install external software, and how to download and pre-process required corpora.

%\subsection{Word Embeddings}
For learning word embeddings we use \texttt{word2vec}; for building our neural netowrk we use Keras, a minimalist, highly modular neural networks library, written in Python and capable of running on top of either TensorFlow or Theano~\cite{chollet2015}; in our case it runs on top of Theano, a Python library that allows to define, optimize, and evaluate mathematical expressions involving multi-dimensional arrays efficiently~\cite{TheTheanoDevelopmentTeam2016}.

The input to our network consists of the concatenation of the word embeddings and the one-hot n-gram representations of the word sequences with the length of the sequence being the whole sentence; this input is feed into a LSTM layer that in turn projects into a fully connected output layer with softmax activation function.

\section{Case Studies}
\label{sec:casestudies}

The implementation from Section~\ref{sec:implementation} was used to participate in the EmpiriST 2015 shared task (see Subsection~\ref{ssec:case_empirist}), and subsequently, to run experiments with different data and parameters for training (see Subsection~\ref{ssec:case_postempirist}).

\emph{empirist}%
\footnote{\url{https://sites.google.com/site/empirist2015/home/shared-task-data}}
is the cmc and web training data containing data samples from different CMC genres and samples from text genres on the web.
The data were tagged by two annotators, and unclear cases were decided by a third person. See Bei{\ss}wenger~\shortcite{empirist2016} for more details.

\emph{Tiger v2.2}%
\footnote{\url{http://www.ims.uni-stuttgart.de/forschung/ressourcen/korpora/tiger.html}}
is version 2.2 of the TIGERCorpus\cite{Brants2004} containing German newspaper texts. 
The corpus was semi-automatically POS-tagged. For research and evaluation purposes, the TIGERCorpus can be downloaded for free.

\emph{de.wiki'15}%
\footnote{\url{http://www1.ids-mannheim.de/kl/projekte/korpora/verfuegbarkeit.html#Download}}
are user talk pages (messages from users to users, often questions and advice) and article talk pages (questions, concerns or comments related to improving a Wikipedia article), and article pages of the German wikipedia from 2015, made available by the \emph{Institut f\"{u}r Deutsche Sprache}\footnote{\url{http://www.ids-mannheim.de}}.
The user talk pages contain
% 378,576,711 
$0.9*10^9$ tokens in
% 15,343,904
$15*10^6$ sentences, the article talk pages
% 446,551,142 
$0.4*10^9$ tokens in
%17,275,385 
$17*10^6$ sentences, and the article pages
% 1,126,462,560 
$1.1*10^9$
tokens in
% 46,740,611 
$46*10^6$ sentences.
% tokens: 378,576,711+446,551,142+1,126,462,560 = 1,951,590,413
% sentences: 15,343,904+17,275,385+46,740,611 = 79359900
The data is available under the 
CC BY-SA 3.0\footnote{Creative Commons Attribution-ShareAlike 3.0 Unported, i.e.~the data can be copied and redistributed, and adapted for any purpose, even commercially. See \url{http://creativecommons.org/licenses/by-sa/3.0/} for more details.} license.

\begin{table}[h]
\begin{center}
\begin{tabular}{l|r|r}
\hline
\multicolumn{1}{c}{}	& \multicolumn{1}{c}{Tokens}	& \multicolumn{1}{c}{Sentences} \\ \hline
empirist    			& $10*10^3$	& $0.6*10^3$      \\ \hline
Tiger v2.2 		& $0.9*10^9$	& $0.05*10^6$	  \\ \hline
de.wiki'15   		& $2.0*10^9$	& $79*10^6$	  \\ \hline\hline
C4Corpus            	& $$		& $$	  \\ \hline
DECOW14           	& $11.7*10^9$	& $600*10^6$	  \\ \hline
\emph{*unclear*}	& $19.9*10^9$	& $1300*10^6$	  \\ \hline
\end{tabular}
\end{center}
\caption{\label{tab:corpora}Training data used for EmpiriST (upper part) and additional data for the subsequent experiments (lower part).}
\end{table}

\emph{C4Corpus}%
\footnote{\url{https://github.com/dkpro/dkpro-c4corpus}}
is a full documents German web corpus that has been extracted from CommonCrawl, the largest publicly available general Web crawl to date. The data is available under the CreativeCommons license family\footnote{\url{https://creativecommons.org/licenses/}}. 
See Habernal~\shortcite{Habernal.et.al.2016.LREC} for details about the corpus construction pipeline, and other information about the corpus.

\emph{DECOW14}%
\footnote{\url{http://corporafromtheweb.org/decow14/}}
is the sentence shuffled German web corpus by COW created with the 2014 technology of the COW initiative~\cite{SchaeferBildhauer2012}.
The data can be used for purposes of academic research.
% $11.7*10^9$ tokens 
% $0.6*10^9$ (624,767,747) sentences

\emph{*unclear*} web corpus.
%DeTenTen
% $19.9*10^9$ (19,918,263,493) tokens
% $1.3*10^9$ (1,309,696,220) sentences

An overview of the used training data can be found in Table~\ref{tab:corpora}.

For evaluation we used the EmpiriST 2015 trial data: 4000 tokens, PoS tagged by one annotator without systematic error checks, i.e.~the accuracy of the PoS annotations is likely lower than on the training data and on the gold standard.

\subsection{EmpiriST 2015}
\label{ssec:case_empirist}

For the three submitted  runs of EmpiriST 2015 we used word embeddings from the \emph{empirist} data (run 1), the \emph{de.wiki'15} data (run 2), and both (run 3). 
We trained a 500-dimensional skip-gram model on the \emph{empirist} data that ignored all words with less than 3 occurrences within a window size of 10; it was trained with negative sampling (value 5) and (accidentally%
\footnote{Although, technically, the two can be combined they 'work against' each other: hierarchical softmax works better with few training epochs but for negative sampling, few training epochs are suboptimal.}% https://groups.google.com/forum/#!topic/word2vec-toolkit/WUWad9fL0jU
) also with hierarchical softmax.
We trained a 500-dimensional continuous bag-of-word model on the \emph{de.wiki'15} data that ignored all words with less than 25 occurrences within a window size of 10; it was trained with negative sampling (value 3) and (accidentally) also with hierarchical softmax.

The rational behind training the two models differently was that according to \texttt{word2vec} author's experience\footnote{\url{https://groups.google.com/d/msg/word2vec-toolkit/NLvYXU99cAM/E5ld8LcDxlAJ}} a skip-gram model "works well with small amount[s] of the training data, [and] represents well even rare words or phrases", and a cbow model is "several times faster to train than the skip-gram, [and has] slightly better accuracy for the frequent words".
% empirist.bin -cbow 0 -size 500 -window 10 -hs 1 -negative 5 -min-count 3 
% bigdata.bin -cbow 1 -size 500 -window 10 -hs 1 -negative 3 -min-count 25
The other parameters of \texttt{word2vec} were left at its default settings.

To optimize the output results of the neural network we ran a simple grid search for the following three parameters: the output dimensions of the hidden LSTM layer, the dropout value for the projections from the LSTM to the output layer during training, and the number of epochs during training. The resulting parameters were $1024$ output dimensions, $0.1$ as the dropout value, and $20$ number of epochs.
%lstm_output_dims = [128, 256, 512, 1024*]
%dropouts = [0.1*, 0.25, 0.5, 0.75]
%nb_epochs = [5, 10, 20*]

For the first run we trained the network on \emph{empirist}, for the second run on \emph{Tiger v2.2}, and for the third on the concatenation of the two. % 
% 1: empirist_training (tagset:ibk)
% 2: tiger-2.2 (tagset:1999)
% 3: empirist_training + tiger-2.2 (tagset:ibk)
Our evaluation on the EmpiriST trial data resulted in these accuracy scores:
1:~$0.88$, 
2:~$0.78$, 
3:~$0.93$;
and the evaluation of the organizers of EmpiriST 2015 was:
1:~$0.84$,
2:~$0.82$,
3:~$0.88$.

\subsection{Post-EmpiriST Experiments}
\label{ssec:case_postempirist}
As a post-EmpiriST addition to the results we wanted to (1)~remedy some errors and oversights in our initial pre-processing and training, (2)~optimize the learning parameters of the word embedding models and the neural network, and (3)~train word embedding models on other data.
%fixme: \fxnote[margin]{add (1)}

The optimal learning parameters for the word embedding models were selected according to a comprehensive set of experiments and comparisons by Levy~\shortcite{TACL570}, and observations and suggestions by Mikolov~\shortcite{arXiv:1310.4546}. For the post-EmpiriST experiments we used the skip-gram with negative-sampling training method (SGNS), with a negative-sampling value of $15$ (and without hierarchical softmax, cf.~Subsection~\ref{ssec:case_empirist}), ignored all words with less than $100$ occurrences within a window size of $10$, and a sub-sampling value of $10^{-5}$. 
% cbow=0, negative=15, hs=0, window=10, sample=10^-5 
% arXiv:1310.4546: -negative 15 -sample 0.00001
% TACL570: alpha=0.75 and dyn=1-> fixed in word2vec algorithm;
% There are quite a few differences between the skip-gram and the CBOW models. However, if you have a lot of training data, their performance should be comparable.\footnote{\url{https://groups.google.com/d/msg/word2vec-toolkit/NLvYXU99cAM/E5ld8LcDxlAJ}}

As additional data to train word embedding models we obtained and processed \emph{C4Corpus}, \emph{DECOW14}, and \emph{*unclear*}.

\fxnote[inline]{}Results pending.

\section{Conclusion \& Outlook}
\label{sec:conclusion}

\fxnote[inline]{}Pending.

%\section*{Acknowledgments}
%The acknowledgments should go immediately before the references.  Do
%not number the acknowledgments section. Do not include this section
%when submitting your paper for review.

\clearpage
% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2016}
%\nocite{*}
\bibliography{paper}
\bibliographystyle{acl2016}

%\appendix
%\section{Supplemental Material}
%\label{sec:supplemental}
%Supplement

\end{document}

### 2016-05-23 paper.tex
paper.{bib,tex} - fix *unclear* status of deTenTen

@@
 DECOW14         & $11.7*10^9$	& $600*10^6$	  \\ \hline
-\emph{*unclear*}	& $19.9*10^9$	& $1300*10^6$	  \\ \hline
+deTenTen	    & $19.9*10^9$	& $1300*10^6$	  \\ \hline
 \end{tabular}
@@
 
-\emph{*unclear*} web corpus.
+\emph{deTenTen} web corpus.
 %DeTenTen
@@
 % $1.3*10^9$ (1,309,696,220) sentences
+\cite{1120431}
 
@@
 
-As additional data to train word embedding models we obtained and processed \emph{C4Corpus}, \emph{DECOW14}, and \emph{*unclear*}.
+As additional data to train word embedding models we obtained and processed \emph{C4Corpus}, \emph{DECOW14}, and \emph{deTenTen}.
 

### 2016-06-10 paper.tex
paper.tex - fix:line length

@@
     implement matured methods -- from natural language processing to achieve
-    competitive results on POS tagging of German CMC and web corpus data; 
-    in particular, the system uses word embeddings and character-level representations of word beginnings and endings in a LSTM recurrent neural
+    competitive results on POS tagging of German CMC and web corpus data; in
+    particular, the system uses word embeddings and character-level
+    representations of word beginnings and endings in a LSTM recurrent neural
     network architecture.
@@
 
-Part-of-speech tagging (and tokenization) is an essential processing stage for virtually all NLP applications.
-However, for German there has been relatively little work in this area so far.
-To this end, the EmpiriST shared task (ST) focuses on tokenization and part-of-speech tagging~\cite{empirist2016}.
+Part-of-speech tagging (and tokenization) is an essential processing stage for
+virtually all NLP applications. However, for German there has been relatively
+little work in this area so far. To this end, the EmpiriST shared task (ST)
+focuses on tokenization and part-of-speech tagging~\cite{empirist2016}.
 
 % Is POS tagging a solved task\cite{Giesbrecht2009}.
-Recently, State-of-the-art results on various linguistic tasks were accomplished by architectures using neural-network based word embeddings; Baroni~\shortcite{baroni-dinu-kruszewski:2014:P14-1} conducted a set of experiments comparing the popular \texttt{word2vec}~\cite{DBLP:journals/corr/abs-1301-3781,arXiv:1310.4546} implementation for creating word embeddings to other recent distributional methods with state-of-the-art results across various (semantic) tasks.
-Even though these results suggest that the word embeddings substantially outperform the recent architectures on semantic similarity and analogy detection tasks Levy~\shortcite{TACL570} conducted a comprehensive set of experiments and comparisons that suggest that much of the improved results are due to the system design and parameter optimizations, rather than the selected method;
-they conclude that "there does not seem to be a consistent significant advantage to one approach over the other".
+Recently, State-of-the-art results on various linguistic tasks were
+accomplished by architectures using neural-network based word embeddings;
+Baroni~\shortcite{baroni-dinu-kruszewski:2014:P14-1} conducted a set of
+experiments comparing the popular
+\texttt{word2vec}~\cite{DBLP:journals/corr/abs-1301-3781,arXiv:1310.4546}
+implementation for creating word embeddings to other recent distributional
+methods with state-of-the-art results across various (semantic) tasks.  Even
+though these results suggest that the word embeddings substantially outperform
+the recent architectures on semantic similarity and analogy detection tasks
+Levy~\shortcite{TACL570} conducted a comprehensive set of experiments and
+comparisons that suggest that much of the improved results are due to the
+system design and parameter optimizations, rather than the selected method;
+they conclude that "there does not seem to be a consistent significant
+advantage to one approach over the other".
 
-We take these results to use \texttt{word2vec} word embeddings in our architecture because they are (1) often faster to learn, and (2) for educational purposes, i.e.~we wanted to get some experience in using them.
+We take these results to use \texttt{word2vec} word embeddings in our
+architecture because they are (1) often faster to learn, and (2) for
+educational purposes, i.e.~we wanted to get some experience in using them.
 
@@
 \label{sec:design}
-Our overall design takes inspiration from as far back as Benello~\shortcite{Benello1989} who used a few preceding and one following word in a feed-forward network with back-propagation for PoS tagging; they achieved an accuracy of $0.95$ on the Brown Corpus.
+Our overall design takes inspiration from as far back as
+Benello~\shortcite{Benello1989} who used a few preceding and one following word
+in a feed-forward network with back-propagation for PoS tagging;
+they achieved an accuracy of $0.95$ on the Brown Corpus.
 
-Further inspiration comes from dos Santos~\shortcite{santos2014learning} who used a deep neural network trained with character-level joint with word embedding representation of words for PoS tagging.
-On the Wall Street Journal (WSJ) portion of the Penn Treebank they achieve accuracy scores of $0.9732$.
+Further inspiration comes from dos Santos~\shortcite{santos2014learning} who
+used a deep neural network trained with character-level joint with word
+embedding representation of words for PoS tagging. On the Wall Street Journal
+(WSJ) portion of the Penn Treebank they achieve accuracy scores of $0.9732$.
 
-Our design comprises character-level 3-grams of word beginnings and ends joint with word embedding representation of words in a long short-term memory (LSTM) recurrent neural network (RNN) architecture~\cite{Hochreiter:1997:LSM:1246443.1246450} for learning a mapping of sequences of these representations to PoS tags.
+Our design comprises character-level 3-grams of word beginnings and ends joint
+with word embedding representation of words in a long short-term memory (LSTM)
+recurrent neural network (RNN)
+architecture~\cite{Hochreiter:1997:LSM:1246443.1246450} for learning a mapping
+of sequences of these representations to PoS tags.
 
@@
 
-We maintain the implementation in a source code repository at \url{https://github.com/iiegn/bot_zen}. 
-The version tagged as {\tt 0.9} comprises the version that was used to generate the results submitted to the ST; 
-the version tagged as {\tt 1.0} is identical at its core but comes with explicit documentation on how to download and install external software, and how to download and pre-process required corpora.
+We maintain the implementation in a source code repository at
+\url{https://github.com/iiegn/bot_zen}.  The version tagged as {\tt 0.9}
+comprises the version that was used to generate the results submitted to the
+ST; 
+the version tagged as {\tt 1.0} is identical at its core but comes with
+explicit documentation on how to download and install external software, and
+how to download and pre-process required corpora.
 
 %\subsection{Word Embeddings}
-For learning word embeddings we use \texttt{word2vec}; for building our neural netowrk we use Keras, a minimalist, highly modular neural networks library, written in Python and capable of running on top of either TensorFlow or Theano~\cite{chollet2015}; in our case it runs on top of Theano, a Python library that allows to define, optimize, and evaluate mathematical expressions involving multi-dimensional arrays efficiently~\cite{TheTheanoDevelopmentTeam2016}.
+For learning word embeddings we use \texttt{word2vec}; for building our neural
+netowrk we use Keras, a minimalist, highly modular neural networks library,
+written in Python and capable of running on top of either TensorFlow or
+Theano~\cite{chollet2015}; in our case it runs on top of Theano, a Python
+library that allows to define, optimize, and evaluate mathematical expressions
+involving multi-dimensional arrays
+efficiently~\cite{TheTheanoDevelopmentTeam2016}.
 
-The input to our network consists of the concatenation of the word embeddings and the one-hot n-gram representations of the word sequences with the length of the sequence being the whole sentence; this input is feed into a LSTM layer that in turn projects into a fully connected output layer with softmax activation function.
+The input to our network consists of the concatenation of the word embeddings
+and the one-hot n-gram representations of the word sequences with the length of
+the sequence being the whole sentence; this input is feed into a LSTM layer
+that in turn projects into a fully connected output layer with softmax
+activation function.
 
@@
 
-The implementation from Section~\ref{sec:implementation} was used to participate in the EmpiriST 2015 shared task (see Subsection~\ref{ssec:case_empirist}), and subsequently, to run experiments with different data and parameters for training (see Subsection~\ref{ssec:case_postempirist}).
+The implementation from Section~\ref{sec:implementation} was used to
+participate in the EmpiriST 2015 shared task (see
+Subsection~\ref{ssec:case_empirist}), and subsequently, to run experiments with
+different data and parameters for training (see
+Subsection~\ref{ssec:case_postempirist}).
 
@@
 \footnote{\url{https://sites.google.com/site/empirist2015/home/shared-task-data}}
-is the cmc and web training data containing data samples from different CMC genres and samples from text genres on the web.
-The data were tagged by two annotators, and unclear cases were decided by a third person. See Bei{\ss}wenger~\shortcite{empirist2016} for more details.
+is the cmc and web training data containing data samples from different CMC
+genres and samples from text genres on the web.
+The data were tagged by two annotators, and unclear cases were decided by a
+third person. See Bei{\ss}wenger~\shortcite{empirist2016} for more details.
 
@@
 \footnote{\url{http://www.ims.uni-stuttgart.de/forschung/ressourcen/korpora/tiger.html}}
-is version 2.2 of the TIGERCorpus\cite{Brants2004} containing German newspaper texts. 
-The corpus was semi-automatically POS-tagged. For research and evaluation purposes, the TIGERCorpus can be downloaded for free.
+is version 2.2 of the TIGERCorpus\cite{Brants2004} containing German newspaper
+texts. 
+The corpus was semi-automatically POS-tagged. For research and evaluation
+purposes, the TIGERCorpus can be downloaded for free.
 
@@
 \footnote{\url{http://www1.ids-mannheim.de/kl/projekte/korpora/verfuegbarkeit.html#Download}}
-are user talk pages (messages from users to users, often questions and advice) and article talk pages (questions, concerns or comments related to improving a Wikipedia article), and article pages of the German wikipedia from 2015, made available by the \emph{Institut f\"{u}r Deutsche Sprache}\footnote{\url{http://www.ids-mannheim.de}}.
+are user talk pages (messages from users to users, often questions and advice)
+and article talk pages (questions, concerns or comments related to improving a
+Wikipedia article), and article pages of the German wikipedia from 2015, made
+available by the \emph{Institut f\"{u}r Deutsche
+Sprache}\footnote{\url{http://www.ids-mannheim.de}}.
 The user talk pages contain
@@
 % sentences: 15,343,904+17,275,385+46,740,611 = 79359900
-The data is available under the 
-CC BY-SA 3.0\footnote{Creative Commons Attribution-ShareAlike 3.0 Unported, i.e.~the data can be copied and redistributed, and adapted for any purpose, even commercially.
-See \url{http://creativecommons.org/licenses/by-sa/3.0/} for more details.} license.
+The data is available under the CC BY-SA 3.0\footnote{Creative Commons
+Attribution-ShareAlike 3.0 Unported, i.e.~the data can be copied and
+redistributed, and adapted for any purpose, even commercially. See
+\url{http://creativecommons.org/licenses/by-sa/3.0/} for more details.}
+license.
 
@@
 \end{center}
-\caption{\label{tab:corpora}Training data used for EmpiriST (upper part) and additional data for the subsequent experiments (lower part).}
-\end{table}
+\caption{\label{tab:corpora}Training data used for EmpiriST (upper part) and
+additional data for the subsequent experiments (lower part).} \end{table}
 
 \emph{C4Corpus}%
-\footnote{\url{https://github.com/dkpro/dkpro-c4corpus}}
-is a full documents German web corpus that has been extracted from CommonCrawl, the largest publicly available general Web crawl to date.
-The data is available under the CreativeCommons license family\footnote{\url{https://creativecommons.org/licenses/}}.
-See Habernal~\shortcite{Habernal.et.al.2016.LREC} for details about the corpus construction pipeline, and other information about the corpus.
+\footnote{\url{https://github.com/dkpro/dkpro-c4corpus}} is a full documents
+German web corpus that has been extracted from CommonCrawl, the largest
+publicly available general Web crawl to date. 
+The data is available under the CreativeCommons license
+family\footnote{\url{https://creativecommons.org/licenses/}}. 
+See Habernal~\shortcite{Habernal.et.al.2016.LREC} for details about the corpus
+construction pipeline, and other information about the corpus.
 
 \emph{DECOW14}%
-\footnote{\url{http://corporafromtheweb.org/decow14/}}
-is the sentence shuffled German web corpus by COW created with the 2014 technology of the COW initiative~\cite{SchaeferBildhauer2012}.
+\footnote{\url{http://corporafromtheweb.org/decow14/}} is the sentence shuffled
+German web corpus by COW created with the 2014 technology of the COW
+initiative~\cite{SchaeferBildhauer2012}.
 The data can be used for purposes of academic research.
@@
 
-For evaluation we used the EmpiriST 2015 trial data: 4000 tokens, PoS tagged by one annotator without systematic error checks, i.e.~the accuracy of the PoS annotations is likely lower than on the training data and on the gold standard.
+For evaluation we used the EmpiriST 2015 trial data: 4000 tokens, PoS tagged by
+one annotator without systematic error checks, i.e.~the accuracy of the PoS
+annotations is likely lower than on the training data and on the gold standard.
 
@@
 
-For the three submitted  runs of EmpiriST 2015 we used word embeddings from the \emph{empirist} data (run 1), the \emph{de.wiki'15} data (run 2), and both (run 3). 
-We trained a 500-dimensional skip-gram model on the \emph{empirist} data that ignored all words with less than 3 occurrences within a window size of 10; it was trained with negative sampling (value 5) and (accidentally%
-\footnote{Although, technically, the two can be combined they 'work against' each other: hierarchical softmax works better with few training epochs but for negative sampling, few training epochs are suboptimal.}% https://groups.google.com/forum/#!topic/word2vec-toolkit/WUWad9fL0jU
+For the three submitted  runs of EmpiriST 2015 we used word embeddings from the
+\emph{empirist} data (run 1), the \emph{de.wiki'15} data (run 2), and both (run
+3).  We trained a 500-dimensional skip-gram model on the \emph{empirist} data
+that ignored all words with less than 3 occurrences within a window size of 10;
+it was trained with negative sampling (value 5) and (accidentally%
+\footnote{Although, technically, the two can be combined they 'work against'
+each other: hierarchical softmax works better with few training epochs but for
+negative sampling, few training epochs are suboptimal.}% https://groups.google.com/forum/#!topic/word2vec-toolkit/WUWad9fL0jU
 ) also with hierarchical softmax.
-We trained a 500-dimensional continuous bag-of-word model on the \emph{de.wiki'15} data that ignored all words with less than 25 occurrences within a window size of 10; it was trained with negative sampling (value 3) and (accidentally) also with hierarchical softmax.
+We trained a 500-dimensional continuous bag-of-word model on the
+\emph{de.wiki'15} data that ignored all words with less than 25 occurrences
+within a window size of 10; it was trained with negative sampling (value 3) and
+(accidentally) also with hierarchical softmax.
 
-The rational behind training the two models differently was that according to \texttt{word2vec} author's experience\footnote{\url{https://groups.google.com/d/msg/word2vec-toolkit/NLvYXU99cAM/E5ld8LcDxlAJ}} a skip-gram model "works well with small amount[s] of the training data, [and] represents well even rare words or phrases", and a cbow model is "several times faster to train than the skip-gram, [and has] slightly better accuracy for the frequent words".
+The rational behind training the two models differently was that according to
+\texttt{word2vec} author's
+experience\footnote{\url{https://groups.google.com/d/msg/word2vec-toolkit/NLvYXU99cAM/E5ld8LcDxlAJ}}
+a skip-gram model "works well with small amount[s] of the training data, [and]
+represents well even rare words or phrases", and a cbow model is "several times
+faster to train than the skip-gram, [and has] slightly better accuracy for the
+frequent words".
 % empirist.bin -cbow 0 -size 500 -window 10 -hs 1 -negative 5 -min-count 3 
@@
 
-To optimize the output results of the neural network we ran a simple grid search for the following three parameters: the output dimensions of the hidden LSTM layer, the dropout value for the projections from the LSTM to the output layer during training, and the number of epochs during training.
-The resulting parameters were $1024$ output dimensions, $0.1$ as the dropout value, and $20$ number of epochs.
+To optimize the output results of the neural network we ran a simple grid
+search for the following three parameters: the output dimensions of the hidden
+LSTM layer, the dropout value for the projections from the LSTM to the output
+layer during training, and the number of epochs during training. The resulting
+parameters were $1024$ output dimensions, $0.1$ as the dropout value, and $20$
+number of epochs.
 %lstm_output_dims = [128, 256, 512, 1024*]
@@
 
-For the first run we trained the network on \emph{empirist}, for the second run on \emph{Tiger v2.2}, and for the third on the concatenation of the two. % 
+For the first run we trained the network on \emph{empirist}, for the second run
+on \emph{Tiger v2.2}, and for the third on the concatenation of the two. % 
 % 1: empirist_training (tagset:ibk)
@@
 \label{ssec:case_postempirist}
-As a post-EmpiriST addition to the results we wanted to (1)~remedy some errors and oversights in our initial pre-processing and training, (2)~optimize the learning parameters of the word embedding models and the neural network, and (3)~train word embedding models on other data.
+As a post-EmpiriST addition to the results we wanted to (1)~remedy some errors
+and oversights in our initial pre-processing and training, (2)~optimize the
+learning parameters of the word embedding models and the neural network, and
+(3)~train word embedding models on other data.
 %fixme: \fxnote[margin]{add (1)}
 
-The optimal learning parameters for the word embedding models were selected according to a comprehensive set of experiments and comparisons by Levy~\shortcite{TACL570}, and observations and suggestions by Mikolov~\shortcite{arXiv:1310.4546}.
-For the post-EmpiriST experiments we used the skip-gram with negative-sampling training method (SGNS), with a negative-sampling value of $15$ (and without hierarchical softmax, cf.~Subsection~\ref{ssec:case_empirist}), ignored all words with less than $100$ occurrences within a window size of $10$, and a sub-sampling value of $10^{-5}$.
+The optimal learning parameters for the word embedding models were selected
+according to a comprehensive set of experiments and comparisons by
+Levy~\shortcite{TACL570}, and observations and suggestions by
+Mikolov~\shortcite{arXiv:1310.4546}. 
+For the post-EmpiriST experiments we used the skip-gram with negative-sampling
+training method (SGNS), with a negative-sampling value of $15$ (and without
+hierarchical softmax, cf.~Subsection~\ref{ssec:case_empirist}), ignored all
+words with less than $100$ occurrences within a window size of $10$, and a
+sub-sampling value of $10^{-5}$. 
 % cbow=0, negative=15, hs=0, window=10, sample=10^-5 
@@
 
-As additional data to train word embedding models we obtained and processed \emph{C4Corpus}, \emph{DECOW14}, and \emph{deTenTen}.
+As additional data to train word embedding models we obtained and processed
+\emph{C4Corpus}, \emph{DECOW14}, and \emph{deTenTen}.
 

### 2016-06-10 paper.tex
paper.{tex,bib} - fix review comments

@@
 \input{bit-aclfinalcopy}
-%\def\aclpaperid{***} %  Enter the acl Paper ID here
+\def\aclpaperid{16} %  Enter the acl Paper ID here
 
@@
 
-\title{Instructions for ACL-2016 Proceedings}
+\title{bot.zen @ EmpiriST 2015 - A minimally-deep learning PoS-tagger \\ (trained for German CMC and Web data)}
 
@@
 
-    The system combines a small assertion of trending techniques -- that
-    implement matured methods -- from natural language processing to achieve
-    competitive results on POS tagging of German CMC and web corpus data; in
+    The system combines a small assertion of trending techniques, which
+    implement matured methods, from natural language processing to achieve
+    competitive results on POS tagging of German CMC and Web corpus data; in
     particular, the system uses word embeddings and character-level
@@
 
-    %fixme: \fxerror[inline]{}write something about the results.
+    \fxerror[inline]{}write something about the results.
 
@@
 
-Part-of-speech tagging (and tokenization) is an essential processing stage for
-virtually all NLP applications. However, for German there has been relatively
-little work in this area so far. To this end, the EmpiriST shared task (ST)
-focuses on tokenization and part-of-speech tagging~\cite{empirist2016}.
+Part-of-speech (POS) tagging is an essential processing stage for virtually all
+NLP applications.
+Subsequent tasks, like for example parsing, named-entity recognition, event
+detection, and machine translation, often utilise POS tags (directly or
+indirectly), and altogether, benefit from accurate tag sequences.
+However, frequent phenomena in computer-mediated communication (CMC) and Web
+corpora such as emoticons, acronyms, interaction words, iteration of letters,
+graphostylistics, shortenings, addressing terms, and non-standard
+spellings~\cite{crystal2001,androutsopoulos2007,beisswenger2013} (gravely)
+deteriorate the performance of POS-taggers~\cite{giesbrecht2009,I13-1041}.
+To this end, the EmpiriST shared task (ST) encouraged the developers of NLP
+applications to adapt their tools and resources for the processing of written
+German CMC and Web data~\cite{empirist2016}.
 
-% Is POS tagging a solved task\cite{Giesbrecht2009}.
 Recently, State-of-the-art results on various linguistic tasks were
@@
 implementation for creating word embeddings to other recent distributional
-methods with state-of-the-art results across various (semantic) tasks.  Even
-though these results suggest that the word embeddings substantially outperform
-the recent architectures on semantic similarity and analogy detection tasks
-Levy~\shortcite{TACL570} conducted a comprehensive set of experiments and
-comparisons that suggest that much of the improved results are due to the
-system design and parameter optimizations, rather than the selected method;
-they conclude that "there does not seem to be a consistent significant
+methods with state-of-the-art results across various (semantic) tasks. 
+Even though these results suggest that the word embeddings substantially
+outperform the recent architectures on semantic similarity and analogy
+detection tasks Levy~\shortcite{TACL570} conducted a comprehensive set of
+experiments and comparisons that suggest that much of the improved results are
+due to the system design and parameter optimizations, rather than the selected
+method; they conclude that "there does not seem to be a consistent significant
 advantage to one approach over the other".
@@
 educational purposes, i.e.~we wanted to get some experience in using them.
+\fixme[margin]{Line 70: "...often faster..." is there some evidence / citation for that?}
+\fixme[margin]{Line 71: "...we wanted to get some experience..." -> nobody cares}
 
@@
 involving multi-dimensional arrays
-efficiently~\cite{TheTheanoDevelopmentTeam2016}.
+efficiently~\cite{Theano2016}.
 
@@
 \footnote{\url{https://sites.google.com/site/empirist2015/home/shared-task-data}}
-is the cmc and web training data containing data samples from different CMC
-genres and samples from text genres on the web.
+is the CMC and Web training data containing data samples from different CMC
+genres and samples from text genres on the Web.
 The data were tagged by two annotators, and unclear cases were decided by a
@@
 \footnote{\url{http://www.ims.uni-stuttgart.de/forschung/ressourcen/korpora/tiger.html}}
-is version 2.2 of the TIGERCorpus\cite{Brants2004} containing German newspaper
+is version 2.2 of the TIGERCorpus~\cite{Brants2004} containing German newspaper
 texts. 
@@
 \footnote{\url{https://github.com/dkpro/dkpro-c4corpus}} is a full documents
-German web corpus that has been extracted from CommonCrawl, the largest
+German Web corpus that has been extracted from CommonCrawl, the largest
 publicly available general Web crawl to date. 
@@
 \footnote{\url{http://corporafromtheweb.org/decow14/}} is the sentence shuffled
-German web corpus by COW created with the 2014 technology of the COW
+German Web corpus by COW created with the 2014 technology of the COW
 initiative~\cite{SchaeferBildhauer2012}.
@@
 
-\emph{deTenTen} web corpus.
+\emph{deTenTen} Web corpus.
 %DeTenTen
@@
 An overview of the used training data can be found in Table~\ref{tab:corpora}.
+\fixme[margin]{Line 187: as far as I know the trial data is part of the training data. Testing
+on this will naturally yield good, you are training on your evaluation data.
+What is the performance on the provided test set?}
 
@@
 ) also with hierarchical softmax.
+\fixme[margin]{Line 208: you should avoid terms like accidental. Is it even possible to use
+negative sampling and hierarchical softmax? To my understanding these
+approaches are different techniques that cannot be combined easily. By quickly
+doublechecking the word2vec source code I think only HS is used if it is
+activated, negative-sampling will be disregarded in this case. The authors
+should check that thoroughly though.}
 We trained a 500-dimensional continuous bag-of-word model on the
@@
 The other parameters of \texttt{word2vec} were left at its default settings.
+\fixme[margin]{Line 223: what are the default settings, i.e. they might change over time, it
+is better to explicitly mention them}
 
@@
 3:~$0.93$;
-and the evaluation of the organizers of EmpiriST 2015 was:
+and the overall ST evaluation was:
 1:~$0.84$,
@@
 3:~$0.88$.
+\fixme[inline]{more verbose results.}
 
@@
 (3)~train word embedding models on other data.
-%fixme: \fxnote[margin]{add (1)}
+\fxnote[margin]{add (1)}
 
+\fixme[margin]{When explaining numbers to the power of 10 write $9x10^8$ instead of $0.9*10^9$, also,
+in running text it is advised to use "900 million" instead.}
 The optimal learning parameters for the word embedding models were selected
@@
 
-\fxnote[inline]{}Results pending.
+\fxnote[inline]{Post EmpiriST experiment results / discussion and conclusion is still missing.}
 

### 2016-06-25 paper.tex
paper.tex - finalise for camera-ready version

--- 2016-06-10 paper.tex
@@
 \newcommand\BibTeX{B{\sc ib}\TeX}
+\usepackage{xspace}
+\newcommand\wtv{\texttt{w2v}\xspace}
 
-\title{Instructions for ACL-2016 Proceedings}
+\title{bot.zen @ EmpiriST 2015 - A minimally-deep learning PoS-tagger \\
+       (trained for German CMC and Web data)}
 
 \author{Egon W.~Stemle \\
-  EURAC \\
+  EURAC research \\
   Bozen-Bolzano, Italy \\
-  {\tt egon.stemle@eurac.edu}} % \\\And
-  %Jennifer-Carmen Frey \\
-  %EURAC \\
-  %Bozen-Bolzano, Italy \\
-  %{\tt jennifercarmen.frey@eurac.edu} \\}
+  {\tt egon.stemle@eurac.edu}}
 
@@
 
-\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \maketitle
-\begin{abstract}
+
+\begin{abstract} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     This article describes the system that participated in the Part-of-speech
@@
 
-    The system combines a small assertion of trending techniques -- that
-    implement matured methods -- from natural language processing to achieve
-    competitive results on POS tagging of German CMC and web corpus data; in
-    particular, the system uses word embeddings and character-level
-    representations of word beginnings and endings in a LSTM recurrent neural
-    network architecture.
+    The system combines a small assertion of trending techniques, which
+    implement matured methods, from NLP and ML to achieve competitive results
+    on PoS tagging of German CMC and Web corpus data; in particular, the system
+    uses word embeddings and character-level representations of word beginnings
+    and endings in a LSTM RNN architecture.  
+    Available labelled data (Tiger v2.2 and EmpiriST) and unlabelled data
+    (German Wikipedia) was used for training.
 
-    %fixme: \fxerror[inline]{}write something about the results.
-
+    The system is available under the APLv2 open-source license.
 \end{abstract}
 
-\section{Introduction}
+\section{Introduction} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \label{sec:intro}
 
-Part-of-speech tagging (and tokenization) is an essential processing stage for
-virtually all NLP applications. However, for German there has been relatively
-little work in this area so far. To this end, the EmpiriST shared task (ST)
-focuses on tokenization and part-of-speech tagging~\cite{empirist2016}.
+Part-of-speech (PoS) tagging is an essential processing stage for virtually all
+NLP applications.
+Subsequent tasks, like parsing, named-entity recognition, event
+detection, and machine translation, often utilise PoS tags, and benefit
+(directly or indirectly) from accurate tag sequences.
+However, frequent phenomena in computer-mediated communication (CMC) and Web
+corpora such as emoticons, acronyms, interaction words, iteration of letters,
+graphostylistics, shortenings, addressing terms, spelling variations, and
+boilerplate%
+~\cite{androutsopoulos2007,BernardiniBaroniEvert2008,beisswenger2013}
+deteriorate the performance of PoS-taggers%
+~\cite{giesbrecht2009,baldwin-EtAl:2013:IJCNLP}.
 
-% Is POS tagging a solved task\cite{Giesbrecht2009}.
-Recently, State-of-the-art results on various linguistic tasks were
-accomplished by architectures using neural-network based word embeddings;
-Baroni~\shortcite{baroni-dinu-kruszewski:2014:P14-1} conducted a set of
+To this end, the EmpiriST shared task (ST) invited developers of NLP
+applications to adapt their tokenisation and PoS tagging tools and resources
+for the processing of written German CMC and Web data~\cite{empirist2016}. 
+The ST was divided into two subtasks, tokenisation and PoS tagging, and
+for each subtask two data sets were provided (see Subsection%
+~\ref{subsec:empirist}).
+The systems were evaluated by the organisers on raw data for the tokenisation
+subtask, and on unlabelled but pre-tokenised data for the PoS tagging subtask
+(both on the same approx.~14,000 tokens).
+
+We participated in the PoS tagging subtask of the ST with our new
+minimally-deep learning PoS-tagger:
+We combine \texttt{word2vec} (\wtv) word embeddings (WEs) with a single-layer
+Long Short Term Memory (LSTM) recurrent neural network (RNN) architecture;
+strictly speaking, \wtv is \emph{shallow}. 
+Therefore we call the combination with a single hidden layer
+\emph{minimally-deep}.  
+The sequence of unlabelled \wtv representations of words is accompanied by
+the sequence of n-grams of the word beginnings and endings, and is fed into the
+RNN which in turn predicts PoS labels.
+
+The paper is organised as follows: We present our system design in
+Section~\ref{sec:design}, the implementation in
+Section~\ref{sec:implementation}, and its evaluation in
+Section~\ref{sec:casestudies}. 
+Section~\ref{sec:conclusion} concludes with an outlook on possible
+implementation improvements.
+
+\section{Design} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{sec:design}
+
+Overall, our design takes inspiration from as far back as~\newcite{Benello1989}
+who used four preceding words and one following word in a feed-forward neural
+network with backpropagation for PoS tagging, builds upon the strong foundation
+laid down by~\newcite{collobert:2011b} for a NN architecture and learning
+algorithm that can be applied to various natural language processing tasks, and
+ultimately is a variation of
+% achieved an accuracy of $0.95$ on the Brown Corpus.
+~\newcite{santos2014learning} who trained a NN for PoS tagging, with 
+character-level and WE representations of words. 
+%On the Wall Street Journal (WSJ) portion of the Penn Treebank they achieve
+%accuracy scores of $0.9732$.
+
+\subsection{Word Embeddings} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Recently, state-of-the-art results on various linguistic tasks were
+accomplished by architectures using neural-network based WEs.
+\newcite{baroni-dinu-kruszewski:2014:P14-1} conducted a set of
 experiments comparing the popular
-\texttt{word2vec}~\cite{DBLP:journals/corr/abs-1301-3781,arXiv:1310.4546}
-implementation for creating word embeddings to other recent distributional
-methods with state-of-the-art results across various (semantic) tasks.  Even
-though these results suggest that the word embeddings substantially outperform
-the recent architectures on semantic similarity and analogy detection tasks
-Levy~\shortcite{TACL570} conducted a comprehensive set of experiments and
-comparisons that suggest that much of the improved results are due to the
-system design and parameter optimizations, rather than the selected method;
-they conclude that "there does not seem to be a consistent significant
+\wtv~\cite{DBLP:journals/corr/abs-1301-3781,arXiv:1310.4546}
+implementation for creating WEs to other distributional methods with
+state-of-the-art results across various (semantic) tasks. 
+These results suggest that the word embeddings substantially
+outperform the other architectures on semantic similarity and analogy
+detection tasks.
+Subsequently,~\newcite{TACL570} conducted a comprehensive set of
+experiments and comparisons that suggest that much of the improved results are
+due to the system design and parameter optimizations, rather than the selected
+method.  
+They conclude that "there does not seem to be a consistent significant
 advantage to one approach over the other".
 
-We take these results to use \texttt{word2vec} word embeddings in our
-architecture because they are (1) often faster to learn, and (2) for
-educational purposes, i.e.~we wanted to get some experience in using them.
+Word embeddings provide high-quality low dimensional vector representations of
+words from large corpora of unlabelled data, and the representations, typically
+computed using NNs, encode many linguistic regularities and
+patterns~\cite{arXiv:1310.4546}.
 
-\section{Design}
-\label{sec:design}
-Our overall design takes inspiration from as far back as
-Benello~\shortcite{Benello1989} who used a few preceding and one following word
-in a feed-forward network with back-propagation for PoS tagging;
-they achieved an accuracy of $0.95$ on the Brown Corpus.
+\subsection{Character-Level Sub-Word Information} %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Further inspiration comes from dos Santos~\shortcite{santos2014learning} who
-used a deep neural network trained with character-level joint with word
-embedding representation of words for PoS tagging. On the Wall Street Journal
-(WSJ) portion of the Penn Treebank they achieve accuracy scores of $0.9732$.
+The morphology of a word is opaque to WEs, and the relatedness of
+the meaning of a lemma's different word forms, i.e.~its different string
+representations, is \emph{not} systematically encoded. 
+This means that in morphologically rich languages with long-tailed frequency
+distributions, even some WE representations for word forms of common
+lemmata may become very poor~\cite{DBLP:journals/corr/KimJSR15}.
 
-Our design comprises character-level 3-grams of word beginnings and ends joint
-with word embedding representation of words in a long short-term memory (LSTM)
-recurrent neural network (RNN)
-architecture~\cite{Hochreiter:1997:LSM:1246443.1246450} for learning a mapping
-of sequences of these representations to PoS tags.
+We agree with~\newcite{santos2014learning}
+and~\newcite{DBLP:journals/corr/KimJSR15} that sub-word information is very
+important for PoS tagging, and therefore we augment the WE representations with
+character-level representations of the word beginnings and endings; thereby, we
+also stay language agnostic---at least, as much as possible---by avoiding the
+need for, often language specific, morphological pre-processing.
 
-\section{Implementation}
+\subsection{Recurrent Neural Network Layer} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Language Models are a central part of NLP.
+They are used to place distributions over word sequences that encode systematic
+structural properties of the sample of linguistic content they are built from,
+and can then be used on novel content, e.g.~to rank it or predict some feature
+on it. 
+For a detailed overview on language modelling research see~\newcite{mikolov2012}.
+
+A straight-forward approach to incorporate WEs into feature-based
+language models is to use the embeddings' vector representations as features.
+%For an overview see, e.g.~\newcite{Turian:2010:WRS:1858681.1858721}.
+Having said that, WEs are also used in neural network architectures, where they
+constitute (part of) the input to the network.
+
+Neural networks (NNs) consist of a large number of simple, highly interconnected
+processing nodes in an architecture loosely inspired by the structure of the
+cerebral cortex of the brain~\cite{oreilly2000}.
+The nodes receive weighted inputs through these connections and \emph{fire}
+according to their individual thresholds of their shared activation function.
+A firing node passes on an activation to all successive connected nodes.
+During learning the input is propagated through the network and the output is
+compared to the desired output. 
+Then, the weights of the connections (and the thresholds) are adjusted
+step-wise so as to more closely resemble a configuration that would produce the
+desired output.
+After all input cases have been presented, the process typically starts over
+again, and the output values will usually be closer to the correct values.
+
+RNNs are NNs where the connections between the elements are directed cycles,
+i.e.~the networks have loops, and this enables them to model sequential
+dependencies of the input.
+However, regular RNNs have fundamental difficulties learning long-term
+dependencies, and special kinds of RNNs need to be used~\cite{Hochreiter1991}; 
+a very popular kind is the so called long short-term memory (LSTM)
+network proposed by~\newcite{Hochreiter:1997:LSM:1246443.1246450}.
+
+\section{Implementation} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \label{sec:implementation}
@@
 We maintain the implementation in a source code repository at
-\url{https://github.com/iiegn/bot_zen}.  The version tagged as {\tt 0.9}
-comprises the version that was used to generate the results submitted to the
-ST; 
-the version tagged as {\tt 1.0} is identical at its core but comes with
+\url{https://github.com/bot-zen/}.  
+The version tagged as {\tt 0.9} comprises the version that was used to generate
+the results submitted to the ST.
+The version tagged as {\tt 1.0} is identical at its core but comes with
 explicit documentation on how to download and install external software, and
@@
 
-%\subsection{Word Embeddings}
-For learning word embeddings we use \texttt{word2vec}; for building our neural
-netowrk we use Keras, a minimalist, highly modular neural networks library,
+Our system feeds WEs and character-level sub-word information into a
+single-layer RNN with a LSTM architecture.
+%Overall, we can benefit with this design not only from available labelled data
+%but also from available general and domain-specific unlabelled data
+
+\subsection{Word Embeddings} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%When computing WEs we keep in mind that \newcite{TACL570} observed that one
+%specific configuration of~\wtv, namely the skip-gram model with negative
+%sampling (SGNS) 
+%"is a robust baseline.  While it might not be the best method for every task,
+%it does not significantly underperform in any scenario. Moreover, SGNS is the
+%fastest method to train, and cheapest (by far) in terms of disk space and
+%memory consumption".
+%Coincidentally,~\newcite{arXiv:1310.4546} also suggest to use SGNS
+We incorporates \wtv's original C implementation for learning WEs%
+\footnote{\url{https://code.google.com/archive/p/word2vec/}}
+in an independent pre-processing step, i.e.~we pro-compute the WEs.
+Then, we use gensim%
+\footnote{\url{https://radimrehurek.com/gensim/}}%
+, a Python tool for unsupervised semantic modelling from plain text, to load
+the data, and to extract the vector representations of the embedded words as
+input to our NN.
+
+\subsection{Character-Level Sub-Word Information} %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Our implementation uses a \emph{one-hot encoding} with a few additional
+features for representing sub-word information.
+The one-hot encoding transforms a categorical feature into a vector where
+the categories are represented by equally many dimensions with binary values.
+We convert a letter to lower-case and use the sets of ASCII characters, digits,
+and punctuation marks as categories for the encoding.
+Then, we add dimensions to represent more binary features like
+\emph{'uppercase'} (was upper-case prior to conversion), \emph{'digit'} (is
+digit), \emph{'punctuation'} (is punctuation mark), \emph{whitespace} (is white
+space, except the new line character; note that this category is usually empty,
+because we expect our tokens to \emph{not} include white space characters), and
+\emph{unknown} (other characters, e.g.~diacritics).
+This results in vectors with more than a single \emph{one-hot} dimension. 
+%
+% - alpha-characters are mapped to lower-case one-hot + 'is-uppercase'
+% - digits are mapped to one-hot + 'is-digit'
+% - punctuation marks are mapped to one-hot + 'is-punctuation'
+% - whitespace (ecxept '\n') characters are mapped to one-hot +
+% 'is-whitespace'
+% - unknowns have their own one-hot
+% * '\n' is treated as new-token-character
+
+\subsection{Recurrent Neural Network Layer} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Our implementation uses Keras, a minimalist, highly modular NNs library,
 written in Python and capable of running on top of either TensorFlow or
-Theano~\cite{chollet2015}; in our case it runs on top of Theano, a Python
-library that allows to define, optimize, and evaluate mathematical expressions
-involving multi-dimensional arrays
-efficiently~\cite{TheTheanoDevelopmentTeam2016}.
+Theano~\cite{chollet2015}. 
+In our case it runs on top of Theano, a Python library that allows to define,
+optimize, and evaluate mathematical expressions involving multi-dimensional
+arrays efficiently~\cite{Theano2016}.
 
-The input to our network consists of the concatenation of the word embeddings
-and the one-hot n-gram representations of the word sequences with the length of
-the sequence being the whole sentence; this input is feed into a LSTM layer
-that in turn projects into a fully connected output layer with softmax
-activation function.
+The input to our network are sequences of the same length as the sentences we
+process.
+During training we group sentences of the same length into batches.
+Each single word in the sequence is represented by its sub-word information and
+two WEs that come from two sources (see Section~\ref{sec:casestudies}).
+%Note that the WEs of the domain-specific corpus may have only been derived
+%from a small corpus.
+Unknown words, i.e.~words without a WE, are mapped to a randomly generated
+vector representation once, and this representation is reused later.
+In Total, each word is represented by $1,800$ features: two times $500$ (WEs),
+and ten times $80$ for two 5-grams (word beginning and ending).
+(If words are shorter than 5 characters their 5-grams are zero-padded.)
 
-\section{Case Studies}
+This sequential input is fed into a LSTM layer that, in turn, projects to a
+fully connected output layer with softmax activation function.
+We use categorical cross-entropy as loss function and backpropagation in
+conjunction with the RMSprop optimization for learning.  
+At the time of writing, this was the Keras default---or the explicitly
+documented option to be used---for our type of architecture.
+
+\section{Case Study} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \label{sec:casestudies}
 
-The implementation from Section~\ref{sec:implementation} was used to
-participate in the EmpiriST 2015 shared task (see
-Subsection~\ref{ssec:case_empirist}), and subsequently, to run experiments with
-different data and parameters for training (see
-Subsection~\ref{ssec:case_postempirist}).
+We used our implementation to participate in the EmpiriST 2015 shared task.
+First, we describe the corpora used for training, and then the specific system
+configuration(s) for the ST.
+%% and subsequently, to run experiments with different data and parameters for
+%%training (see Subsection~\ref{ssec:case_postempirist}).
+%Following, a short description of the data we used for training.
 
-\emph{empirist}%
-\footnote{\url{https://sites.google.com/site/empirist2015/home/shared-task-data}}
-is the cmc and web training data containing data samples from different CMC
-genres and samples from text genres on the web.
-The data were tagged by two annotators, and unclear cases were decided by a
-third person. See Bei{\ss}wenger~\shortcite{empirist2016} for more details.
-
+\subsection{Training Data for \wtv and PoS Tagging} %%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Tiger v2.2 (PoS)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \emph{Tiger v2.2}%
 \footnote{\url{http://www.ims.uni-stuttgart.de/forschung/ressourcen/korpora/tiger.html}}
-is version 2.2 of the TIGERCorpus\cite{Brants2004} containing German newspaper
+is version 2.2 of the TIGERCorpus~\cite{Brants2004} containing German newspaper
 texts. 
-The corpus was semi-automatically POS-tagged. For research and evaluation
-purposes, the TIGERCorpus can be downloaded for free.
+The corpus was semi-automatically PoS tagged, and is one of the standard
+corpora used for German PoS tagging. 
+It contains 888,238 tokens in 50,472 sentences.
+For research and evaluation purposes, the TIGERCorpus can be downloaded for
+free.
 
+\subsubsection{German Wikipedia (\wtv)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \emph{de.wiki'15}%
 \footnote{\url{http://www1.ids-mannheim.de/kl/projekte/korpora/verfuegbarkeit.html#Download}}
-are user talk pages (messages from users to users, often questions and advice)
-and article talk pages (questions, concerns or comments related to improving a
+are user talk pages (messages from users to users, often questions and advice),
+article talk pages (questions, concerns or comments related to improving a
 Wikipedia article), and article pages of the German wikipedia from 2015, made
@@
 Sprache}\footnote{\url{http://www.ids-mannheim.de}}.
-The user talk pages contain
-% 378,576,711 
-$0.9*10^9$ tokens in
-% 15,343,904
-$15*10^6$ sentences, the article talk pages
-% 446,551,142 
-$0.4*10^9$ tokens in
-%17,275,385 
-$17*10^6$ sentences, and the article pages
-% 1,126,462,560 
-$1.1*10^9$
-tokens in
-% 46,740,611 
-$46*10^6$ sentences.
+%% user talk pages
+%% 378,576,711 toks
+%% 15,343,904 s
+%%
+%% article talk pages
+%% 446,551,142 toks 
+%% 17,275,385 s
+%%
+%% article pages
+%% 1,126,462,560 toks
+%% 46,740,611 s
+%%
 % tokens: 378,576,711+446,551,142+1,126,462,560 = 1,951,590,413
-% sentences: 15,343,904+17,275,385+46,740,611 = 79359900
-The data is available under the CC BY-SA 3.0\footnote{Creative Commons
+% sentences: 15,343,904+17,275,385+46,740,611 = 79,359,900
+The corpus contains 2 billion tokens 
+(talk:379m, article talk:447m, article:1,1bn) 
+in 79 million sentences 
+(talk:15m, article talk:17m, article:47m), is well-sized for \wtv, and
+also (partly) resembles or target data.
+It is available under the CC BY-SA 3.0\footnote{Creative Commons
 Attribution-ShareAlike 3.0 Unported, i.e.~the data can be copied and
@@
 
+\subsubsection{EmpiriST 2015 Data (PoS and \wtv)} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{subsec:empirist}
+\emph{empirist}%
+\footnote{\url{https://sites.google.com/site/empirist2015/home/shared-task-data}}
+is the CMC and Web data made available by the organizers of the ST.
+It contains data samples from different CMC genres and samples from text genres
+on the Web.
+The training corpus contains 10,053 tokens and was PoS tagged by two annotators
+(unclear cases were decided by a third person). 
+The trial corpus contains around 3,600 tokens (2,100 CMC%
+\footnote{For evaluation during the development phase we used
+    \emph{empirist}-trial.
+    Unfortunately, we found out only later that the CMC part of the trial data
+    is also part of the training data, i.e.~for the CMC data our evaluation
+    data was identical with the training data.}%
+, 1,500 Web) and was PoS tagged by one annotator (without systematic error
+checks%
+%, i.e.~the accuracy of the PoS annotations is likely lower than on the
+%training data and on the ST final evaluation data
+).
+See~\newcite{empirist2016} for more details.
+
+%An overview of the used training data can be found in Table~\ref{tab:corpora}.
+
+%\begin{table}[h]
+%\begin{center}
+%\begin{tabular}{l|r|r}
+%\hline
+%\multicolumn{1}{c}{} & \multicolumn{1}{c}{Tokens} & \multicolumn{1}{c}{Sentences} \\ \hline
+%empirist       & $10*10^3$     & $0.6*10^3$    \\ \hline
+%Tiger v2.2     & $0.9*10^9$    & $0.05*10^6$   \\ \hline\hline
+%de.wiki'15   	& $2.0*10^9$    & $79*10^6$     \\ \hline
+%%C4Corpus      & $$            & $$            \\ \hline
+%%DECOW14       & $11.7*10^9$   & $600*10^6$    \\ \hline
+%%deTenTen	    & $19.9*10^9$   & $1300*10^6$   \\ \hline
+%\end{tabular}
+%\end{center}
+%\caption{\label{tab:corpora}Training data used for the EmpiriST 2015 shared
+%    task. The PoS tags of the upper two corpora were used for training.
+%    % (upper part) and additional data for the subsequent experiments (lower
+%    % part).
+%} \end{table}
+
+%\emph{C4Corpus}%
+%\footnote{\url{https://github.com/dkpro/dkpro-c4corpus}} is a full documents
+%German Web corpus that has been extracted from CommonCrawl, the largest
+%publicly available general Web crawl to date. 
+%The data is available under the CreativeCommons license
+%family\footnote{\url{https://creativecommons.org/licenses/}}. 
+%See Habernal~\shortcite{Habernal.et.al.2016.LREC} for details about the corpus
+%construction pipeline, and other information about the corpus.
+%
+%\emph{DECOW14}%
+%\footnote{\url{http://corporafromtheweb.org/decow14/}} is the sentence shuffled
+%German Web corpus by COW created with the 2014 technology of the COW
+%initiative~\cite{SchaeferBildhauer2012}.
+%The data can be used for purposes of academic research.
+%% $11.7*10^9$ tokens 
+%% $0.6*10^9$ (624,767,747) sentences
+%
+%\emph{deTenTen} Web corpus.
+%%DeTenTen
+%% $19.9*10^9$ (19,918,263,493) tokens
+%% $1.3*10^9$ (1,309,696,220) sentences
+%\cite{1120431}
+
+\subsection{EmpiriST 2015 shared task} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\label{ssec:case_empirist}
+
+For the ST we used one overall configuration for the system, but we used three
+different corpus configurations for training.
+Consequently, we participated in the ST with three runs:
+we used PoS tags from \emph{empirist} (run 1), from \emph{Tiger v2.2} (run 2),
+and from both (run 3).  
+For \wtv we trained a 500-dimensional skip-gram model on \emph{empirist} that
+ignored all words with less than 3 occurrences within a window size of 10;
+it was trained with negative sampling (value 5) and erroneously%
+\footnote{%
+    According to \wtv's author, technically negative sampling and
+    hierarchical softmax can be combined but one should avoid combining them~%
+    (see~\url{https://groups.google.com/forum/#!topic/word2vec-toolkit/WUWad9fL0jU}).
+
+    We had forgotten to deactivate an option in a data processing script.
+}
+also with hierarchical softmax.
+We also trained a 500-dimensional continuous bag-of-words model on
+\emph{de.wiki'15} that ignored all words with less than 25 occurrences within a
+window size of 10; it was trained with negative sampling (value 3) and
+erroneously also with hierarchical softmax.
+
+The rational behind training the two models differently was that according to
+\wtv author's experience%
+\footnote{\url{https://groups.google.com/d/msg/word2vec-toolkit/NLvYXU99cAM/E5ld8LcDxlAJ}}
+a skip-gram model "works well with small amount[s] of the training data, [and]
+represents well even rare words or phrases", and a cbow model is "several times
+faster to train than the skip-gram, [and has] slightly better accuracy for the
+frequent words".
+The other \wtv parameters were left at their default settings%
+\footnote{\texttt{-sample 1e-3 -iter 5 -alpha 0.025} for skip-gram and
+\texttt{-alpha 0.05} for continuous bag-of-words}.
+% empirist.bin -cbow 0 -size 500 -window 10 -hs 1 -negative 5 -min-count 3 
+% bigdata.bin -cbow 1 -size 500 -window 10 -hs 1 -negative 3 -min-count 25
+
+To optimize the system's output we ran a simple grid search for three
+parameters: the hidden LSTM layer's size, the dropout value for the projections
+from the LSTM to the output layer during training, and the number of epochs
+during training. 
+The found values were size:$1024$, dropout:$0.1$, epochs:$20$.
+%lstm_output_dims = [128, 256, 512, 1024*]
+%dropouts = [0.1*, 0.25, 0.5, 0.75]
+%nb_epochs = [5, 10, 20*]
+
 \begin{table}[h]
@@
 \hline
-\multicolumn{1}{c}{}	& \multicolumn{1}{c}{Tokens}	& \multicolumn{1}{c}{Sentences} \\ \hline
-empirist    			& $10*10^3$	& $0.6*10^3$      \\ \hline
-Tiger v2.2 		& $0.9*10^9$	& $0.05*10^6$	  \\ \hline
-de.wiki'15   	& $2.0*10^9$	& $79*10^6$	  \\ \hline\hline
-C4Corpus            	& $$		& $$	  \\ \hline
-DECOW14         & $11.7*10^9$	& $600*10^6$	  \\ \hline
-deTenTen	    & $19.9*10^9$	& $1300*10^6$	  \\ \hline
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{CMC} & \multicolumn{1}{c}{Web} \\ \hline
+(1) \emph{empirist}             & $81.03$       & $86.97$ \\ \hline
+(2) \emph{Tiger v2.2}           & $73.56$       & $89.73$ \\ \hline
+(3) \emph{empirist}+\emph{Tiger v2.2} & $85.42$ & $90.63$ \\ \hline\hline
+Winning Team                    & $87.33$       & $93.55$ \\ \hline
 \end{tabular}
 \end{center}
-\caption{\label{tab:corpora}Training data used for EmpiriST (upper part) and
-additional data for the subsequent experiments (lower part).} \end{table}
+\caption{\label{tab:results}Official results of our PoS tagger for the three
+runs on the EmpiriST 2015 shared task data.
+} 
+\end{table}
 
-\emph{C4Corpus}%
-\footnote{\url{https://github.com/dkpro/dkpro-c4corpus}} is a full documents
-German web corpus that has been extracted from CommonCrawl, the largest
-publicly available general Web crawl to date. 
-The data is available under the CreativeCommons license
-family\footnote{\url{https://creativecommons.org/licenses/}}. 
-See Habernal~\shortcite{Habernal.et.al.2016.LREC} for details about the corpus
-construction pipeline, and other information about the corpus.
+%The official results are listed in Table~\ref{tab:results}.
 
-\emph{DECOW14}%
-\footnote{\url{http://corporafromtheweb.org/decow14/}} is the sentence shuffled
-German web corpus by COW created with the 2014 technology of the COW
-initiative~\cite{SchaeferBildhauer2012}.
-The data can be used for purposes of academic research.
-% $11.7*10^9$ tokens 
-% $0.6*10^9$ (624,767,747) sentences
-
-\emph{deTenTen} web corpus.
-%DeTenTen
-% $19.9*10^9$ (19,918,263,493) tokens
-% $1.3*10^9$ (1,309,696,220) sentences
-\cite{1120431}
-
-An overview of the used training data can be found in Table~\ref{tab:corpora}.
-
-For evaluation we used the EmpiriST 2015 trial data: 4000 tokens, PoS tagged by
-one annotator without systematic error checks, i.e.~the accuracy of the PoS
-annotations is likely lower than on the training data and on the gold standard.
-
-\subsection{EmpiriST 2015}
-\label{ssec:case_empirist}
-
-For the three submitted  runs of EmpiriST 2015 we used word embeddings from the
-\emph{empirist} data (run 1), the \emph{de.wiki'15} data (run 2), and both (run
-3).  We trained a 500-dimensional skip-gram model on the \emph{empirist} data
-that ignored all words with less than 3 occurrences within a window size of 10;
-it was trained with negative sampling (value 5) and (accidentally%
-\footnote{Although, technically, the two can be combined they 'work against'
-each other: hierarchical softmax works better with few training epochs but for
-negative sampling, few training epochs are suboptimal.}% https://groups.google.com/forum/#!topic/word2vec-toolkit/WUWad9fL0jU
-) also with hierarchical softmax.
-We trained a 500-dimensional continuous bag-of-word model on the
-\emph{de.wiki'15} data that ignored all words with less than 25 occurrences
-within a window size of 10; it was trained with negative sampling (value 3) and
-(accidentally) also with hierarchical softmax.
-
-The rational behind training the two models differently was that according to
-\texttt{word2vec} author's
-experience\footnote{\url{https://groups.google.com/d/msg/word2vec-toolkit/NLvYXU99cAM/E5ld8LcDxlAJ}}
-a skip-gram model "works well with small amount[s] of the training data, [and]
-represents well even rare words or phrases", and a cbow model is "several times
-faster to train than the skip-gram, [and has] slightly better accuracy for the
-frequent words".
-% empirist.bin -cbow 0 -size 500 -window 10 -hs 1 -negative 5 -min-count 3 
-% bigdata.bin -cbow 1 -size 500 -window 10 -hs 1 -negative 3 -min-count 25
-The other parameters of \texttt{word2vec} were left at its default settings.
-
-To optimize the output results of the neural network we ran a simple grid
-search for the following three parameters: the output dimensions of the hidden
-LSTM layer, the dropout value for the projections from the LSTM to the output
-layer during training, and the number of epochs during training. The resulting
-parameters were $1024$ output dimensions, $0.1$ as the dropout value, and $20$
-number of epochs.
-%lstm_output_dims = [128, 256, 512, 1024*]
-%dropouts = [0.1*, 0.25, 0.5, 0.75]
-%nb_epochs = [5, 10, 20*]
-
-For the first run we trained the network on \emph{empirist}, for the second run
-on \emph{Tiger v2.2}, and for the third on the concatenation of the two. % 
 % 1: empirist_training (tagset:ibk)
@@
 % 3: empirist_training + tiger-2.2 (tagset:ibk)
-Our evaluation on the EmpiriST trial data resulted in these accuracy scores:
-1:~$0.88$, 
-2:~$0.78$, 
-3:~$0.93$;
-and the evaluation of the organizers of EmpiriST 2015 was:
-1:~$0.84$,
-2:~$0.82$,
-3:~$0.88$.
+%Our evaluation on the EmpiriST trial data resulted in these accuracy scores:
+%1:~$0.88$, 
+%2:~$0.78$, 
+%3:~$0.93$;
+%and the overall ST evaluation was:
+%1:~$0.84$,
+%2:~$0.82$,
+%3:~$0.88$.
 
-\subsection{Post-EmpiriST Experiments}
-\label{ssec:case_postempirist}
-As a post-EmpiriST addition to the results we wanted to (1)~remedy some errors
-and oversights in our initial pre-processing and training, (2)~optimize the
-learning parameters of the word embedding models and the neural network, and
-(3)~train word embedding models on other data.
-%fixme: \fxnote[margin]{add (1)}
+%\subsection{Post-EmpiriST Experiments}
+%\label{ssec:case_postempirist}
+%As a post-EmpiriST addition to the results we wanted to (1)~remedy some errors
+%and oversights in our initial pre-processing and training, (2)~optimize the
+%learning parameters of the word embedding models and the neural network, and
+%(3)~train word embedding models on other data.
+%\fxnote[margin]{add (1)}
+%
+%The optimal learning parameters for the word embedding models were selected
+%according to a comprehensive set of experiments and comparisons by
+%Levy~\shortcite{TACL570}, and observations and suggestions by
+%Mikolov~\shortcite{arXiv:1310.4546}. 
+%For the post-EmpiriST experiments we used the skip-gram with negative-sampling
+%training method (SGNS), with a negative-sampling value of $15$ (and without
+%hierarchical softmax, cf.~Subsection~\ref{ssec:case_empirist}), ignored all
+%words with less than $100$ occurrences within a window size of $10$, and a
+%sub-sampling value of $10^{-5}$. 
+%% cbow=0, negative=15, hs=0, window=10, sample=10^-5 
+%% arXiv:1310.4546: -negative 15 -sample 0.00001
+%% TACL570: alpha=0.75 and dyn=1-> fixed in word2vec algorithm;
+%%There are quite a few differences between the skip-gram and the CBOW models.
+%%However, if you have a lot of training data, their performance should be
+%%comparable.%
+%%\footnote{\url{https://groups.google.com/d/msg/word2vec-toolkit/NLvYXU99cAM/E5ld8LcDxlAJ}}
+%
+%As additional data to train word embedding models we obtained and processed
+%\emph{C4Corpus}, \emph{DECOW14}, and \emph{deTenTen}.
+%
+%\fixme[inline]{The system is said to be trained on various widely available
+%    corpora of German such as Tiger 2.2, DECOW148 etc. It is not discussed in
+%    any detail and thus does not become clear why these corpora were selected
+%    and especially what the systematic benefit of using these different data
+%    sets was; more specifically, the paper does not systematically explore the
+%    diversity of the data and their contribution to a learning improvement on
+%    the system. A section with a systematic evaluation is missing and so is a
+%    section with a more thorough discussion as to why this particular approach
+%    was selected. It is suggested to the authors to provide more background on
+%    these questions.}
 
-The optimal learning parameters for the word embedding models were selected
-according to a comprehensive set of experiments and comparisons by
-Levy~\shortcite{TACL570}, and observations and suggestions by
-Mikolov~\shortcite{arXiv:1310.4546}. 
-For the post-EmpiriST experiments we used the skip-gram with negative-sampling
-training method (SGNS), with a negative-sampling value of $15$ (and without
-hierarchical softmax, cf.~Subsection~\ref{ssec:case_empirist}), ignored all
-words with less than $100$ occurrences within a window size of $10$, and a
-sub-sampling value of $10^{-5}$. 
-% cbow=0, negative=15, hs=0, window=10, sample=10^-5 
-% arXiv:1310.4546: -negative 15 -sample 0.00001
-% TACL570: alpha=0.75 and dyn=1-> fixed in word2vec algorithm;
-% There are quite a few differences between the skip-gram and the CBOW models.
-However, if you have a lot of training data, their performance should be comparable.\footnote{\url{https://groups.google.com/d/msg/word2vec-toolkit/NLvYXU99cAM/E5ld8LcDxlAJ}}
-
-As additional data to train word embedding models we obtained and processed
-\emph{C4Corpus}, \emph{DECOW14}, and \emph{deTenTen}.
-
-\fxnote[inline]{}Results pending.
-
-\section{Conclusion \& Outlook}
+\section{Conclusion \& Outlook} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \label{sec:conclusion}
 
-\fxnote[inline]{}Pending.
+We presented our submission to the EmpiriST 2015 shared task, where we
+participated in the PoS tagging sub-task with fair results on the CMC data and
+adequate results on the Web data. 
+Still, our implementation, albeit following state-of-the art designs and methods, is
+quite unpolished, and can certainly gain performance with more detailed tuning.
+For example, adding special sequence start and sequence stop symbols to the
+input is typically done as a pre-processing step, which might improve the
+results at the beginning and the end of sentences;
+or we might gain some performance by adding additional hidden layers to enable
+the network to learn more intermediate abstractions.
+A more profound design change could also help, e.g.~Recurrent Memory Network
+are a novel recurrent architecture that have been shown to outperform LSTMs on
+some language modelling tasks.
+%and sentence completion tasks, while also allowing insights into the data from
+%a linguistic perspective~\newcite{tran-bisazza-monz:2016:N16-1}.
+Finally, for learning the word embeddings we could use different corpora, or
+selectively extract parts from large web-corpora resembling---as much as
+possible---the type of data that is to be tagged.
 
-%\section*{Acknowledgments}
+%\section*{Acknowledgments} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %The acknowledgments should go immediately before the references.  Do
@@
 
-\clearpage
-% include your own bib file like this:
-%\bibliographystyle{acl}
-%\bibliography{acl2016}
+% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\clearpage
 %\nocite{*}
+\bibliographystyle{acl2016}
 \bibliography{paper}
-\bibliographystyle{acl2016}
 
-%\appendix
+%\appendix %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\section{Supplemental Material}

### 2016-06-28 paper.tex
paper.tex - camera-ready version
paper.tex - add hyperref options:linkcolor,pdfmetas

@@
 
-\title{bot.zen @ EmpiriST 2015 - A minimally-deep learning PoS-tagger \\
+\newcommand{\mytitle}{bot.zen @ EmpiriST 2015 - A minimally-deep learning PoS-tagger \\
     (trained for German CMC and Web data)}
+\newcommand{\mypdftitle}{\mytitle}
+\newcommand{\mypdfsubject}{in Proceedings of the 10th Web as Corpus Workshop
+    (WAC-X) and the EmpiriST Shared Task}
+\newcommand{\mystitle}{bot.zen - A minimally-deep learning PoS-tagger}
+\newcommand{\mykeywords}{PoS tagger, word empbeddings, word2vec, neural
+    network, RNN, LSTM, EmpiriST 2015 shared task}
+\newcommand{\mypdfkeywords}{\mykeywords}
+
+%%%% hyper & options
+\definecolor{darkred}{rgb}{0.5,0,0}
+\definecolor{darkgreen}{rgb}{0,0.5,0}
+\definecolor{darkblue}{rgb}{0,0,0.5}
+
+\usepackage[final=true, pdfstartview=FitH]{hyperref}
+\hypersetup{
+    pdftitle={\mypdftitle},
+    pdfauthor={egon w. stemle <egon.stemle@eurac.edu>},
+    pdfsubject={\mypdfsubject},
+    pdfkeywords={\mypdfkeywords},
+    setpagesize=true,
+    colorlinks=true,
+    linkcolor=darkred,
+    urlcolor=darkblue,
+    citecolor=darkgreen
+}
+
+\title{\mytitle}
 
@@
     and endings in a LSTM RNN architecture.  
-    Available labelled data (Tiger v2.2 and EmpiriST) and unlabelled data
-    (German Wikipedia) was used for training.
+    Labelled data (Tiger v2.2 and EmpiriST) and unlabelled data (German
+    Wikipedia) were used for training.
 

### 2016-06-28 paper.tex
paper.{bib,tex} - fix and add links to refs,footnotes

@@
 \emph{de.wiki'15}%
-\footnote{\url{http://www1.ids-mannheim.de/kl/projekte/korpora/verfuegbarkeit.html#Download}}
+\footnote{\url{http://www1.ids-mannheim.de/kl/projekte/korpora/verfuegbarkeit.html\#Download}}
 are user talk pages (messages from users to users, often questions and advice),
@@
     hierarchical softmax can be combined but one should avoid combining them~%
-    (see~\url{https://groups.google.com/forum/#!topic/word2vec-toolkit/WUWad9fL0jU}).
+    (see~\url{https://groups.google.com/forum/\#!topic/word2vec-toolkit/WUWad9fL0jU}).
 
@@
 %\nocite{*}
+\small
 \bibliographystyle{acl2016}
 \bibliography{paper}
+\normalsize
 
